Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
nudges

\paragraph{Property specification}
Next, we describe the specific property that we pass to the program
synthesiser as the specification $\sigma$.  There are two different
algorithms in DSVerifier that can be used for stability
verification~\cite{daes20161,Bessa16}, one based on
Schur's decomposition and another one based on Jury's
criteria~\cite{astrom1997computer}.  Here, we choose Jury's
method~\cite{astrom1997computer}, due to its efficiency.

@@

\paragraph{Use of fixed-point computation in the program synthesis engine}
The program synthesis engine uses fixed-point arithmetic.
Namely, we use the domain $\mathbb{R}\param{I}{F}$
for the controller's coefficients and the domain 
$\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.
Note that $I$ and $F$, as well as $I_b$ and $F_b$, 
denote the integer and fractional size, respectively, with
$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
%in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
%where $I$ and $F$ denote the integer and fractional size, respectively.
%Regarding the plant, its coefficients are this is synthesised over the 
%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
%denote the order of the polynomials representing the 
%numerator and denominator of the plant's transfer function, respectively. 
%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (CEGIS paradigm). 
\label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation} \label{sec:experiments}

>>>>

\paragraph{Specification of the stability property}

Next, we describe the specific property that we pass to the program
synthesiser as the specification $\sigma$.  There are two different
algorithms in DSVerifier that can be used for stability
verification~\cite{daes20161,Bessa16}, one based on
Schur's decomposition and another one based on Jury's
criteria~\cite{astrom1997computer}.  Here, we choose Jury's
method~\cite{astrom1997computer}, due to its efficiency.

@@

\paragraph{Fixed-point computation in program synthesis}

The program synthesis engine uses fixed-point arithmetic.  Namely, we use
the domain $\mathbb{R}\param{I}{F}$ for the controller's coefficients and
the domain $\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.  Note
that $I$ and $F$, as well as $I_b$ and $F_b$, denote the integer and
fractional size, respectively, with $\mathbb{R}\langle I_b,F_b \rangle
\supseteq \mathbb{R}\langle I,F \rangle$.
%
%the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
%in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
%where $I$ and $F$ denote the integer and fractional size, respectively.
%Regarding the plant, its coefficients are this is synthesised over the 
%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
%denote the order of the polynomials representing the 
%numerator and denominator of the plant's transfer function, respectively. 
%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis of Closed-loop System (Step~D)
\label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation} \label{sec:experiments}
